Tutorial: SQL-on-Hadoop Systems

### 2015-04-02 paper.tex
Formats

Even though the driver that enables all the system presented in this tutorial to work in a single cluster environment is the shared file system, Hadoop File System (HDFS), there is actually a variety of file format that are being used to store data.

Most file formats are variants of PAX \cite{AilamakiDHS01}

\noindent{\bf Text}. By far the most popular file format is of course plain text.

\vspace{2mm}
\noindent{\bf Avro}.

\vspace{2mm}
\noindent{\bf RC}.

\vspace{2mm}
\noindent{\bf ORC and DRWF}.

\vspace{2mm}
\noindent{\bf Parquet}.

>>>>

Even though the driver that enables all the system presented in this tutorial to work in a single cluster environment is the shared file system, Hadoop File System (HDFS), there is actually a variety of file format that are being used to store data. 
By far the most popular file format is of course plain text.
But there are other options, most of them being variants of PAX \cite{AilamakiDHS01}. For example, Avro, sequence, RC, ORC and DRWF, as well as Parquet.
We present them and perform a comparison between them in terms of usability, data size (compression) and speed of processing
